Investigation of ant cuticle dataset using image texture analysis

### 2022-09-21 paper/main.tex
change k-views paragraph

For the feasibility study in this ant image datasets, we tested the statistical
clusterings methods and deep learning methods separately. Both K-means and
K-views were used for statistical clustering methods. The experiments may
indicate how well the statistical approach and deep learning networks will do in
this type of textural images. In pre-processing the dataset for the statistical
clustering methods, we apply the Gabor filter to transform the gray-scale ant
image into four Gabor-filtered channels, subtract the gray-scale image from each
channel, and take the absolute value of the resulting images. This
pre-processing will highlight some of characteristic features in textures, such
as edge-like in the image. This step is very useful in feeding the datasets to
the K-views algorithms. The theta $\theta$ parameters in the Gabor filters used
are multiples of $\pi/4$ radians starting from $0$ to $\pi$ radians. The Gabor
filter lambda $\lambda$ parameter is equal to $\pi$. In order to classify an
image with K-views or K-means we count the number of pixels assigned to each
cluster.

In our experiments, we use $k=3$ clusters; one for background, and the other two
as rough and smooth. To determine if an image is rough or smooth, we choose the
cluster with the majority number of pixels. The number of pixels assigned to the
background cluster are ignored for classification.

% \subsection{Deep learning models used for the experiments}

>>>>

For the feasibility study in these ant image datasets, we tested the statistical
clustering methods and deep learning methods separately. Both K-means and
K-views were used for statistical clustering methods. The experiments may
indicate how well the statistical approach and deep learning networks will do in
this type of textural images. A pre-processing step of the dataset for the
statistical clustering methods is shown below. This pre-processing will
highlight some of characteristic features in textures, such as edge-like in the
image. This step is very useful in feeding the datasets to the K-views
algorithms. In order to classify an image with K-views or K-means in which we
count the number of pixels assigned to each cluster. A brief procedure for
K-views experiments is given below for training and classification.
\begin{description}
    \item[Step 1:] Pre-processing the dataset: apply the Gabor filter to
          transform the gray-scale ant image into four Gabor-filtered channels,
          subtract the gray-scale image from each channel, and take the absolute
          value of the resulting images. The theta θ parameters in the Gabor
          filters used are multiples of π/4 radians starting from 0 to π
          radians. The Gabor filter lambda λ parameter is equal to π.

    \item[Step 2:] Initialize k = 3 clusters; one for background, and the other
          two as rough and smooth.

    \item[Step 3:] Extract patches for each cluster for the clustering.

    \item[Step 4:] Calculate the mean of each cluster once the training
          converges.

    \item[Step 5:] Use the mean of the cluster for the classification. To
          determine if an image is rough or smooth, we choose the cluster with
          the majority number of pixels. The number of pixels assigned to the
          background cluster are ignored for classification.
\end{description}

\noindent Steps 2 to 4 are for training and step 5 is for the classification.
For the K-means experiments, it will be the same as the K-views except no
patches are used.
\newline
% \subsection{Deep learning models used for the experiments}
